### 2015-05-13 corral.tex
update

\medskip\noindent\textbf{Sound Partial-Order Reduction }
%
By default, \corral instruments a \texttt{yield} statement (which denotes a potential nondeterministic context-switch) before every shared memory access of each thread. It then leverages sequentialization to explore all possible thread interleavings up to a pre-defined bound. Our approach to accelerating \corral is simple and yet effective: we simplify the sequentialization that \corral performs by instrumenting \texttt{yield} statements only at shared memory accesses that \whoop reported as potentially racy.\footnote{In the presence of data races and relaxed memory, even considering all interleavings of shared memory accesses may be insufficient to find all bugs.} This effectively acts as a partial-order reduction that can significantly reduce the number of interleavings that \corral needs to explore, and thus increase performance and scalability.

@@

We now show that our partial-order reduction is sound: it does not miss any more bugs than what \corral would miss even without taking advantage of the \whoop race-related information. Let \corral run an $n$ amount of entry point pairs with yields in all \emph{visible} operations (synchronization points and shared memory accesses). Let this configuration be known as $C$. Each entry point pair is running in a separate \corral process. \corral will miss all bugs that are triggered by more than 3 threads running concurrently and all bugs that are triggered by investigating a larger than $r$ recursion bound and larger than $k$ context-switch bound. Let \corral then run the same $n$ amount of pairs, but this time \whoop removes the \texttt{yield} statements in all non-racy shared memory accesses. Let this configuration be known as $W+C$. Because these shared memory accesses cannot race, performing a \texttt{yield} will not introduce any new program behaviors. Thus, \corral will find the same bugs using the configuration $W+C$, as using the configuration $C$.

>>>>

\medskip\noindent\textbf{Sound Partial-Order Reduction }
%
By default, and assuming no race-freedom guarantees, \whoop instruments a \texttt{yield} statement (which denotes a potential nondeterministic context-switch) after each shared memory access of each entry point.\footnote{In the presence of data races and relaxed memory, even considering all interleavings of shared memory accesses may be insufficient to find all bugs.} \whoop then sends this instrumented program to \corral, which leverages sequentialization to explore all possible thread interleavings up to a pre-defined bound. Our approach to accelerating \corral is simple and yet effective: we simplify the sequentialization that \corral performs by instrumenting \texttt{yield} statements only at shared memory accesses that \whoop reported as potentially racy. This effectively acts as a partial-order reduction that can significantly reduce the number of interleavings that \corral needs to explore, and thus increase performance and scalability.

@@

We now show that our partial-order reduction is sound: it does not miss any more bugs than what \corral would miss even without taking advantage of the \whoop race-related information. Let \corral run an $n$ amount of entry point pairs with yields after all \emph{visible} operations (synchronization points and shared memory accesses). Let this configuration be known as $C$. Each entry point pair is running in a separate \corral process. \corral will miss all bugs that are triggered by more than 3 threads running concurrently and all bugs that are triggered by investigating a larger than $r$ recursion bound and larger than $k$ context-switch bound. Let \corral then run the same $n$ amount of pairs, but this time \whoop removes the \texttt{yield} statements after all non-racy shared memory accesses. Let this configuration be known as $W+C$. Because these shared memory accesses cannot race, performing a \texttt{yield} will not introduce any new program behaviors. Thus, \corral will find the same bugs using the configuration $W+C$, as using the configuration $C$.
